---
pagetitle: "2027 AP-LS Preconference Workshops"
css: ../index.css
listing:
    contents:
      - "**/*.qmd"
    type: grid
    grid-columns: 2
    categories: false
    sort-ui: false
    filter-ui: false
    fields: [title, subtitle, categories]
---

<!--
STAGE 2: when workshops are confirmed (expected Fall 2026), add one
folder per workshop by copying conferences/_template/preconference/workshop_1/
and editing its front matter. The grid below fills in automatically.
Once workshops exist, set sort-ui and filter-ui above to true.
-->

```{r setup, include=FALSE}
# Workshop rates and notes come from conferences/data/*.csv, refreshed from
# the conference Google Sheet by conferences/_update-conference.R.
library(readr)
library(dplyr)
data_dir <- file.path(dirname(knitr::current_input(dir = TRUE)), "..", "data")
conf_info <- read_csv(file.path(data_dir, "info.csv"),
                      col_types = cols(.default = "c"), show_col_types = FALSE)
info <- setNames(as.list(conf_info$value), conf_info$key)
info <- lapply(info, function(x) if (is.na(x)) "" else x)
workshop_rates <- read_csv(file.path(data_dir, "workshop-rates.csv"),
                           col_types = cols(.default = "c"),
                           show_col_types = FALSE)
rate_table <- function(day_type) {
  workshop_rates |>
    filter(type == day_type) |>
    select(status, early_bird, regular) |>
    knitr::kable(col.names = c("Status", "Early Bird (before Jan 31)",
                               "Regular (after Feb 1)"),
                 align = "lcc")
}
```

::: column-screen
::: hero-banner
::: content-block
::: heading-guard
:::
# Preconference Workshops {.h4}
[Wednesday, March 17, 2027]{.h6}


::: hero-buttons
[{{< fa arrow-left-long aria-hidden="true" >}} Back to Conference](../index.qmd){.btn-action .btn .btn-success role="button"}
:::

:::
:::
:::



## {{< fa circle-info >}}Pricing Information{#price}

::: {.panel-tabset .box-shadow}
### REGISTRATION RATES & INCLUSIONS

*`r info$workshop_rates_note`*

#### Full-Day Workshop Rates

```{r}
#| echo: false
#| results: asis
cat(rate_table("Full-Day"), sep = "\n")
```

#### Half-Day Workshop Rates

```{r}
#| echo: false
#| results: asis
cat(rate_table("Half-Day"), sep = "\n")
```
:::

## Descriptions & Details{#details}

> `r info$preconference_note`

*Attendees register for preconference workshops with their conference registration.*

::: {#workshops}
:::
