---
pagetitle: "20XX AP-LS Preconference Workshops"
css: ../index.css
listing:
    contents:
      - "**/*.qmd"
    type: grid
    grid-columns: 2
    categories: false
    sort-ui: false
    filter-ui: false
    fields: [title, subtitle, categories]
---

<!--
================================================================
PRECONFERENCE WORKSHOPS SUB-PAGE
================================================================
Workshops come from the workshops tab of the conference Google
Sheet. Add a row per workshop, then run
source("conferences/_update-conference.R"): it writes each
workshop's folder (workshop_1, workshop_2, ...) and this grid fills
in on its own. Once workshops exist, set sort-ui and filter-ui
above to true.

Rates and notes come from the workshop-rates and info tabs of the
same Sheet. The old copy-paste-a-workshop-folder method still works
if you need a one-off page: copy
conferences/_template/preconference/workshop_1/ and edit its front
matter by hand.
================================================================
-->

```{r setup, include=FALSE}
# Sheet-driven rates and notes, refreshed by
# conferences/_update-conference.R.
library(readr)
library(dplyr)
data_dir <- file.path(dirname(knitr::current_input(dir = TRUE)), "..", "data")
conf_info <- read_csv(file.path(data_dir, "info.csv"),
                      col_types = cols(.default = "c"), show_col_types = FALSE)
info <- setNames(as.list(conf_info$value), conf_info$key)
info <- lapply(info, function(x) if (is.na(x)) "" else x)
workshop_rates <- read_csv(file.path(data_dir, "workshop-rates.csv"),
                           col_types = cols(.default = "c"),
                           show_col_types = FALSE)
rate_table <- function(day_type) {
  workshop_rates |>
    filter(type == day_type) |>
    select(status, early_bird, regular) |>
    knitr::kable(col.names = c("Status", "Early Bird (before Jan 31)",
                               "Regular (after Feb 1)"),
                 align = "lcc")
}
```

::: column-screen
::: hero-banner
::: content-block
::: heading-guard
:::
# Preconference Workshops {.h4}
[Wednesday, March D, 20XX]{.h6}


::: hero-buttons
[{{< fa arrow-left-long aria-hidden="true" >}} Back to Conference](../index.qmd){.btn-action .btn .btn-success role="button"}
:::

:::
:::
:::



## {{< fa circle-info >}}Pricing Information{#price}

::: {.panel-tabset .box-shadow}
### REGISTRATION RATES & INCLUSIONS

*`r info$workshop_rates_note`*

#### Full-Day Workshop Rates

```{r}
#| echo: false
#| results: asis
cat(rate_table("Full-Day"), sep = "\n")
```

#### Half-Day Workshop Rates

```{r}
#| echo: false
#| results: asis
cat(rate_table("Half-Day"), sep = "\n")
```
:::

## Descriptions & Details{#details}

> `r info$preconference_note`

*Attendees register for preconference workshops with their conference registration.*

<!-- When the workshop flyer PDF exists, uncomment the download button
     and add its link.
[download {{< fa arrow-right-long aria-hidden="true" >}}](https://WORKSHOP-FLYER-URL){.btn .btn-outline-primary .ml-auto role="button"}
-->

::: {#workshops}
:::
