---
title: "Getting started with aplsr"
vignette: >
  %\VignetteIndexEntry{Getting started with aplsr}
  %\VignetteEngine{quarto::html}
  %\VignetteEncoding{UTF-8}
format: html
---

```{r}
#| include: false
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
```

## Why this package exists

The AP-LS website is a Quarto site, and its pages shared a single
script, `assets/apls_functions.R`, that every page loaded with `source()`. As the
site grew, the same helpers were copied into individual pages, and the copies
drifted apart. `aplsr` collects those helpers in one place so a page can load
them with `library(aplsr)` and call one tested function on every page.

The package covers three kinds of helper: tables of award recipients, small
HTML/UI components, and a data-frame utility.

```{r}
#| label: setup
library(aplsr)
```

## Award tables

Each award page reads a CSV of past recipients and renders it with one function.
`awards_table()` handles the common case of one or more named recipients per
year.

```{r}
#| label: awards-table
saleem <- data.frame(
  year = c(2026, 2026, 2025),
  name = c("Alicia Nijdam-Jones", "Laura Smalarz", "Miko Wilford")
)
awards_table(saleem)
```

Pass `detail` to add a muted second column, for example an award type or a
mentor:

```{r}
#| label: awards-table-detail
teaching <- data.frame(
  year = c(2026, 2026),
  name = c("Deah Quinlivan", "Cassandra Bailey"),
  note = c("Outstanding Teaching & Mentoring", "Early Career Teaching & Mentoring")
)
awards_table(teaching, detail = "note")
```

Two awards have their own layout. `book_awards_table()` shows the year, author,
and a linked title, and `dissertation_table()` lays out first, second, and third
place across columns.

```{r}
#| label: book-table
books <- data.frame(
  year = "2026",
  author = "David DeMatteo & Kelly C. Scherr (Eds.)",
  title = "The Oxford Handbook of Psychology and Law",
  url = "https://doi.org/10.1093/oxfordhb/9780197649138.001.0001",
  img = ""
)
book_awards_table(books)
```

```{r}
#| label: dissertation-table
diss <- data.frame(
  year = 2026,
  first = "Sandy S. Xie",
  second = "Samantha Rea Bean",
  third = "Luca Adolfo Tiberi"
)
dissertation_table(diss)
```

All three share one look through `apls_table_theme()`, so a change there updates
every award page at once.

## HTML and UI helpers

`carousel()` builds a Bootstrap image carousel from a list of slides:

```{r}
#| label: carousel
#| eval: false
slides <- list(
  list(caption = "2026 conference", image = "img/2026.jpg", link = "conferences/")
)
carousel("gallery", duration = 5000, items = slides)
```

`create_inline_object()` returns an inline icon and link, and
`generate_info_bar()` returns an info-bar block; both return HTML strings you can
drop into a page with `cat()` or an inline R expression.

```{r}
#| label: inline
create_inline_object("envelope", "Email the office", "mailto:office@ap-ls.org")
```

## Using a function on a page

A page chunk reads its data and calls the matching function:

```{r}
#| label: page-usage
#| eval: false
library(aplsr)

data <- read.csv("../data/saleem-shah.csv")
awards_table(data, name = "name")
```

The recipient CSVs themselves are refreshed from the awards Google Sheet by the
site's `awards/_update-awards.R` script, which is separate from this package.
